How to Avoid OOTA Without Really Trying

### 2024-09-01 paper/ootavacuous.tex
paper/ootavacuous: Drop table of contents and rework header
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
paper/ootavacuous: Anonymize authors for review process
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{document}
\title{P3064R2: How to Avoid OOTA Without Really Trying}

@@

\author{
Alan Stern\\{\small \email{stern@rowland.harvard.edu}} \and
Paul E.~McKenney\\{\small \email{paulmck@kernel.org}} \and
Michael Wong\\{\small \email{fraggamuffin@gmail.com}} \and
Maged Michael\\{\small \email{maged.michael@gmail.com}}
}
\date{July 12, 2024 (Post-St. Louis)}
\maketitle{}

Audience: SG1

@@

\pagebreak

\tableofcontents

\pagebreak

>>>>

\begin{document}
\title{How to Avoid OOTA Without Really Trying}

@@

% Blind review process.
% \author{
% Alan Stern\\{\small \email{stern@rowland.harvard.edu}} \and
% Paul E.~McKenney\\{\small \email{paulmck@kernel.org}} \and
% Michael Wong\\{\small \email{fraggamuffin@gmail.com}} \and
% Maged Michael\\{\small \email{maged.michael@gmail.com}}
% }
\maketitle{}

@@
